% -%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%
% MDI200: Probabilités                            %  
% Devoir 1                                        %
% Data:05/10/2011                                 %
% Paris,France                                    % 
% Groupe:                                         %
% - Tiago Chedraoui Silva                   % 
% -%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%

\documentclass[a4paper,12pt]{article}

\usepackage[english,listings,algo]{tcs}

% Cover %
\def \ttprofname{Penelope POULTON} % teachers name
\def \ttabrv{ANG206} % abbreviation of names class
\def \ttabrvxt{Cycle d'harmonisation } % period
\def \mytitle{A new ally against cancer} % Big title
\def \mysubtitle{Tutorial english class - Second Semester of 2011 } % subtitle
\def \ttauth{Tiago Chedraoui Silva} % author's name
\def \ttxt{Rack: 214 } % Extra text right side of name
\def \ttdate{November 3, 2011} % date

\begin{document}
\titleTMB 
\newpage


\section{New Words}

% Write the meanings in english-english form  
\begin{description}

%\item[Okayed] %- aprovar

%\item[Enlisted] %- alistar

\item[Blunt]  {\it(adjective)} - Saying what you think without trying to be polite or caring about other people’s feelings.
%brusco
%    blunt criticism
%    Blunt and outspoken, he often quarreled with fellow officials.


\item[Dash] {\it(verb)} - To move quickly.
%(sumiram rapidamente)
%along aside - cautiously


\item[Endeavor] {\it(noun)} - An effort or attempt to do something.
% Writing is a very different endeavor than teaching.
% indévãr =P

\item[Halt] {\it(verb)} - To stop something, or to bring something to a stop.
%    [I] "Halt!" ordered the guard.
%    [T] Congress voted additional funds in an effort to halt the spread of the disease.
%    [T] Nationwide, mail delivery was halted by the strike.
%parada

\item[Harsh] {\it(adjective)} - Unkind or cruel.
%severo, desagradável
%harsh criticism

\item[Lifespan] {\it(noun)} - The length of time for which a person, animal or thing exists.
% duração de vida
%The average human lifespan in the developed countries has increased over the last hundred years.
%The project's lifespan is estimated at about five years.

\item[Markedly] {\it(adverb)} - Obvious or noticeable.
%   There was a marked improvement in my health when I started exercising.
%signitificamente


\item[Prod] {\it(verb)} - To prod someone is to encourage someone to take action, esp. when
  the person is slow or unwilling.
%No matter how much I prod he will not tell me what happened.
% estimular
% for instance por exemplo


\item[Pointedly] {\it(adverb)} - In an obvious and intentional way.
% claramente
% She pointedly ignored him.

\item[Subdue] {\it(verb)} - To reduce the force of something, or to prevent something from existing or developing.
% She’d be hard to subdue if she got mad.
%The fire burned for eight hours before the fire crews could subdue it.
%He criticized the school for trying to subdue individual expression.



%strain - tensão 
%something that causes anxiety, worry, or difficulty:
%    [U] Loss of funding has put a lot of strain on the day-care center.
%    [C] The benefits of keeping our daughter at home make the strains of having only one income worthwhile.

%brew- fermento 


%\item[Out of favour] - Investments, products, or services that are out of favour are no longer popular with investors or consumers.
%    Shares in the out-of-favour telecommunications sector fell from 391p to 246p yesterday.
%    fall/remain/go out of favour While the markets' attention remains firmly focused on the yen, the euro has fallen out of favor.
%    be out of favour with sb/sth Airline stocks are currently out of favour with institutional investors because of the global economic slowdown.
%fell out of favor - caiu em desuso
%\item[Tweak] -to pull and twist something with a small sudden movement
%Standing in front of the mirror she tweaked a strand of hair into place.

%\item[plague] - To cause someone or something difficulty or suffering, esp. repeatedly or continually.
%    Financial problems have been plaguing the company.
%    That pain in my shoulder is plaguing me again.

%\item[setback] - Something that causes delay or stops progress.
%    Democrats suffered a serious setback in yesterday’s election, losing all three contested seats.


\end{description}

\section{Glossary}

\begin{description}
\item[Antigen]  Biology a  harmful substance  that  causes the  body to  produce
  antibodies, which are substances that fight disease
\item[Cancer] A disease in which cells in the body grow without control, or a serious medical condition caused by this disease.
\item[CD8+ T cell] Cells responsable for killing tumors
\item[CD4+ T cell] Cells that give orders about who and what to  attack to the
  foot soldiers.
\item[FDA] - Food and Drug Administration
\item[Tumors] A mass  of cells in the  body that grow faster than  usual and can
  cause illness.
\end{description}


% Intro
% New vaccine with chomoeterapy
%
%
\newpage

\spc{2} % double spacing

\section{Text with words}

In 1950, we were one billion, in 1975 were four billion, nowadays, human race has reached an incredible number of seven billion people
living  in the  same blued-planet  called Earth  and it  is projected  to exists fifteen
billion in 2050.  {\color{red}Pointedly}, thanks to the increase
of  {\color{red}lifespan}, which was possible, mainly, by the development of medicine, we were
able to achieve such impressive numbers.

Nevertheless, Earth has limited resources, in a way that, in a very near future, it
will  be no  more available  to everyone.  We  are going  to live  in period  of
shortage, some places will not have potable water, others will run out of food,
or will not have enough space neither to  drive a car nor to live alone. As long
as   people  are   concerned  about   this  possible   problem,  an   effort  to
{\color{red}halt} these increase of population  is needed. Probably, we will see
some {\color{red}harsh} actions to be taken by countries to {\color{red}subdue} the problem of overpopulation.

 Indeed, this is  a global problem and not a national  one; so we will
need to  forget our differences in  culture, religion, language; and  we have to
start to work together. We need to change the world, even though sometimes we have to be steady and give up the thing we
want the  most, even our  dreams. Maybe, we  are not concerned about  the future,
because probably we will not live in this near future, however it will be the era
of our children. In spite of your parents and grandparents have not been concerned
about this  problem, if  they had  the knowledge of  the consequences  caused by
their acts they would have done things differently. Then, its our opportunity to
change our acts, our laws, our thoughts.

For example, maybe this is a {\color{red}blunt} criticism, but catholic church's idea of not allowing
the use of preservatives during a sexual relationship should be no more accepted
by  population,   otherwise  we  will  {\color{red}dash}  into   a  way  without
exit. We need to be aware of the consequences our acts result in, and preventing
an undesired baby  is not only a desire to a couple but, today,  as it concerns
everyone, it is a need of the world so it can be in equilibrium.

Finally, if you know someone who thinks differently, we just ask you to try to {\color{red}prod} him
to think about what  is going to happen to our, yet  beautiful, planet, and what
each person could do, it being a big {\color{red}endeavor} or not, to get us out of this situation.
If you do it, and other people too, we are going to create a chain, which will
little by  little {\color{red}markedly} change the situation.  

\end{document}